Counterfactual Training: Teaching Models Plausible and Actionable Explanations

### 2025-03-06 paper/preprint/paper.tex
more work on appendix

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, breakable, left=2mm, colback=white, coltitle=black, bottomtitle=1mm, rightrule=.15mm, colframe=quarto-callout-warning-color-frame, toprule=.15mm, bottomrule=.15mm, arc=.35mm, titlerule=0mm, title=\textcolor{quarto-callout-warning-color}{\faExclamationTriangle}\hspace{0.5em}{Warning}, opacityback=0, leftrule=.75mm, toptitle=1mm, colbacktitle=quarto-callout-warning-color!10!white]

@Cynthia, @Arie, I have tentatively phrased the above in terms of a
theorem and proof. This is something I've so far shied away from because
I feel a bit out of my depth when it comes to mathematical proofs. The
above makes intuitive sense to me, but I don't know for sure if it's
correct.

@@

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, breakable, left=2mm, colback=white, coltitle=black, bottomtitle=1mm, rightrule=.15mm, colframe=quarto-callout-warning-color-frame, toprule=.15mm, bottomrule=.15mm, arc=.35mm, titlerule=0mm, title=\textcolor{quarto-callout-warning-color}{\faExclamationTriangle}\hspace{0.5em}{Warning}, opacityback=0, leftrule=.75mm, toptitle=1mm, colbacktitle=quarto-callout-warning-color!10!white]

@Cynthia, @Arie, I'm including some preliminary results here but will
rerun experiments in the coming days. You'll notice some odd outlier
results (huge values) for the initial grid search
(Section~\ref{sec-app-initial}). My belief is that this is once again
due to \emph{ECCo} overshooting for some hyperparameter choices, that we
have discussed before. A simple solution to this story is to actually
impose domain constraints. Let's see what the final results show us (I
also still plan to make slight changes to the implementation), but in
any case I think it might even be worth to report results for the
initial grid search in the final appendix (they do include good results
for CT for certain hyperparameter ranges and highlight limitations
inherited from energy-based modelling).

@@

\begin{tcolorbox}[enhanced jigsaw, opacitybacktitle=0.6, breakable, left=2mm, colback=white, coltitle=black, bottomtitle=1mm, rightrule=.15mm, colframe=quarto-callout-note-color-frame, toprule=.15mm, bottomrule=.15mm, arc=.35mm, titlerule=0mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, opacityback=0, leftrule=.75mm, toptitle=1mm, colbacktitle=quarto-callout-note-color!10!white]

@Cynthia, @Arie, Figure~\ref{fig-mnist} shows much more plausible
(faithful) counterfactuals for a model with CT than the model with
conventional training (Figure~\ref{fig-mnist-vanilla}). In fact, this is
not even using \emph{ECCo+} and still showing better results than the
best results we achieved in our AAAI paper for JEM ensembles.

@@

\subsection{Initial Grid Search}\label{sec-app-initial}

For the initial round of experiments we employed a different training
objective and procedure that led to promising results for some
hyperparameter choices, but suffered from training instabilities.

@@

The hyperparameter grids for the first investigation of the effect of
generator parameters are shown in
Parameters~\ref{exr-gen-params-first-run-train} and
Parameters~\ref{exr-gen-params-first-run-eval}.

\begin{exercise}[Training
Phase]\protect\hypertarget{exr-gen-params-first-run-train}{}\label{exr-gen-params-first-run-train}

@@

  \begin{itemize}
  \tightlist
  \item
    Decisiono. Threshold: \texttt{0.75,\ 0.9,\ 0.95}
  \item
    \(\lambda_{\text{cost}}\): \texttt{0.0,\ 0.1}
  \item
    \(\lambda_{\text{div}}\): \texttt{0.1,\ 0.5,\ 1.0,\ 10.0}
  \item
    Maximum Iterations: \texttt{5,\ 25,\ 50}
  \item
    Optimizerimizer: \texttt{sgd}
  \end{itemize}
\item
  Generator: \texttt{ecco,\ generic,\ revise}
\item
  Training Parameters:

  \begin{itemize}
  \tightlist
  \item
    Objective: \texttt{full,\ vanilla}
  \end{itemize}
\end{itemize}

@@

\begin{exercise}[Evaluation
Phase]\protect\hypertarget{exr-gen-params-first-run-eval}{}\label{exr-gen-params-first-run-eval}

@@

  \begin{itemize}
  \tightlist
  \item
    Convergence: \texttt{max\_iter}
  \item
    Maximum Iterations: \texttt{100}
  \item
    No.~Individuals: \texttt{100}
  \item
    No.~Runs: \texttt{5}
  \end{itemize}
\item
  Generator Parameters:

  \begin{itemize}
  \tightlist
  \item
    \(\lambda_{\text{cost}}\): \texttt{0.0}
  \item
    \(\lambda_{\text{div}}\):
    \texttt{0.1,\ 0.5,\ 1.0,\ 5.0,\ 10.0,\ 20.0}
  \item
    Learning Rate: \texttt{1.0}
  \item
    Maximum Iterations: \texttt{50}
  \item
    Optimizerimizer: \texttt{sgd}
  \end{itemize}
\end{itemize}

@@

@@

\begin{itemize}
\tightlist
\item
  \textbf{Energy Penalty} (Table~\ref{tbl-lin_sep-lambda_energy_exper}):
  \emph{ECCo} generally does yield better results than \emph{Vanilla}
  for higher choices of the energy penalty (10,15) during training.
  \emph{Generic} performs poorly accross the board. \emph{Omni} seems to
  have an anchoring effect, in that it never performs terribly but also
  never as good as the best \emph{ECCo} results. \emph{REVISE} performs
  poorly across the board.
\item
  \textbf{Cost} (Table~\ref{tbl-lin_sep-lambda_cost_exper}): Results for
  all generators (except \emph{Omni}) are quite bad, which can likely be
  attributed to extremely bad results for some choices of the
  \textbf{Energy Penalty} (results here are averaged). For \emph{ECCo}
  and \emph{Generic}, higher cost values generally lead to worse
  results.
\item
  \textbf{Maximum Iterations}: No clear patterns recognizable, so it
  seems that smaller choices are ok.
\item
  \textbf{Validity}: \emph{ECCo} almost always valid except for very low
  values during training and high values at evaluation time.
  \emph{Generic} often has poor validity.
\item
  \textbf{Accuracy}: Seems largely unaffected.
\end{itemize}

\begin{longtable}{ccccc}

@@

  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{div}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{div}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0.01 & \textit{ECCo} & $-9.91 \cdot 10^{11}$ & $2.25 \cdot 10^{12}$ \\
  full & 0.01 & \textit{Generic} & $-5.71 \cdot 10^{17}$ & $1.3 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.01}} & \color{blue}{\textbf{REVISE}} & \color{blue}{\textbf{-15.6}} & \color{blue}{\textbf{13.2}} \\
  vanilla & 0.01 & \textit{ECCo} & -4.28 & 3.52 \\
  vanilla & 0.01 & \textit{Generic} & -4.45 & 3.47 \\
  vanilla & 0.01 & \textit{REVISE} & -4.91 & 4.24 \\
  full & 0.05 & \textit{ECCo} & $-5.63 \cdot 10^{5}$ & $1.28 \cdot 10^{6}$ \\
  full & 0.05 & \textit{Generic} & $-8.35 \cdot 10^{17}$ & $1.9 \cdot 10^{18}$ \\
  full & 0.05 & \textit{REVISE} & -15 & 12.6 \\
  vanilla & 0.05 & \textit{ECCo} & -4.4 & 3.66 \\
  \color{blue}{\textbf{vanilla}} & \color{blue}{\textbf{0.05}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-4.38}} & \color{blue}{\textbf{3.48}} \\
  vanilla & 0.05 & \textit{REVISE} & -4.94 & 4.22 \\
  full & 0.1 & \textit{ECCo} & $-6.74 \cdot 10^{5}$ & $1.53 \cdot 10^{6}$ \\
  full & 0.1 & \textit{Generic} & $-1.71 \cdot 10^{11}$ & $3.9 \cdot 10^{11}$ \\
  full & 0.1 & \textit{REVISE} & -15.6 & 13.2 \\
  vanilla & 0.1 & \textit{ECCo} & -4.28 & 3.52 \\
  vanilla & 0.1 & \textit{Generic} & -4.45 & 3.48 \\
  vanilla & 0.1 & \textit{REVISE} & -4.91 & 4.25 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.5}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-11.8}} & \color{blue}{\textbf{9.83}} \\
  full & 0.5 & \textit{Generic} & $-1.06 \cdot 10^{18}$ & $2.42 \cdot 10^{18}$ \\
  full & 0.5 & \textit{REVISE} & -15 & 12.6 \\
  vanilla & 0.5 & \textit{ECCo} & -4.4 & 3.65 \\
  vanilla & 0.5 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 0.5 & \textit{REVISE} & -4.95 & 4.22 \\
  full & 1 & \textit{ECCo} & -11.5 & 11.1 \\
  full & 1 & \textit{Generic} & $-1.71 \cdot 10^{11}$ & $3.88 \cdot 10^{11}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{1}} & \color{blue}{\textbf{REVISE}} & \color{blue}{\textbf{-15.7}} & \color{blue}{\textbf{13.3}} \\
  vanilla & 1 & \textit{ECCo} & -4.28 & 3.51 \\
  vanilla & 1 & \textit{Generic} & -4.44 & 3.47 \\
  vanilla & 1 & \textit{REVISE} & -4.91 & 4.25 \\
  full & 5 & \textit{ECCo} & -3.99 & 3.12 \\
  full & 5 & \textit{Generic} & $-4.88 \cdot 10^{17}$ & $1.11 \cdot 10^{18}$ \\
  full & 5 & \textit{REVISE} & -14.6 & 12.1 \\
  vanilla & 5 & \textit{ECCo} & -4.4 & 3.65 \\
  \color{blue}{\textbf{vanilla}} & \color{blue}{\textbf{5}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-4.38}} & \color{blue}{\textbf{3.48}} \\
  vanilla & 5 & \textit{REVISE} & -4.95 & 4.22 \\
  full & 10 & \textit{ECCo} & -2.31 & 0.735 \\
  full & 10 & \textit{Generic} & $-1.7 \cdot 10^{11}$ & $3.86 \cdot 10^{11}$ \\
  full & 10 & \textit{REVISE} & -15.5 & 13 \\
  vanilla & 10 & \textit{ECCo} & -4.28 & 3.51 \\
  vanilla & 10 & \textit{Generic} & -4.44 & 3.47 \\
  vanilla & 10 & \textit{REVISE} & -4.91 & 4.24 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{15}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-2.01}} & \color{blue}{\textbf{0.488}} \\
  full & 15 & \textit{Generic} & $-4.91 \cdot 10^{17}$ & $1.12 \cdot 10^{18}$ \\
  full & 15 & \textit{REVISE} & -14.4 & 11.7 \\
  vanilla & 15 & \textit{ECCo} & -4.4 & 3.65 \\
  vanilla & 15 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 15 & \textit{REVISE} & -4.95 & 4.23 \\\bottomrule

\begin{longtable}{ccccc}

\caption{\label{tbl-lin_sep-lambda_cost_exper}Results for Linearly
Separable data by cost penalty.}

  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{cost}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{cost}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0 & \textit{ECCo} & $-5.32 \cdot 10^{3}$ & $1.21 \cdot 10^{4}$ \\
  full & 0 & \textit{Generic} & $-1.03 \cdot 10^{18}$ & $2.34 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0}} & \color{blue}{\textbf{REVISE}} & \color{blue}{\textbf{-15.4}} & \color{blue}{\textbf{12.9}} \\
  vanilla & 0 & \textit{ECCo} & -4.34 & 3.58 \\
  vanilla & 0 & \textit{Generic} & -4.41 & 3.48 \\
  vanilla & 0 & \textit{REVISE} & -4.93 & 4.23 \\
  full & 0.001 & \textit{ECCo} & -362 & 811 \\
  full & 0.001 & \textit{Generic} & $-2.65 \cdot 10^{17}$ & $6.04 \cdot 10^{17}$ \\
  full & 0.001 & \textit{REVISE} & -15.5 & 13 \\
  vanilla & 0.001 & \textit{ECCo} & -4.34 & 3.58 \\
  \color{blue}{\textbf{vanilla}} & \color{blue}{\textbf{0.001}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-4.41}} & \color{blue}{\textbf{3.48}} \\
  vanilla & 0.001 & \textit{REVISE} & -4.93 & 4.23 \\
  full & 0.1 & \textit{ECCo} & $-3.72 \cdot 10^{11}$ & $8.46 \cdot 10^{11}$ \\
  full & 0.1 & \textit{Generic} & $-4.48 \cdot 10^{14}$ & $1.02 \cdot 10^{15}$ \\
  full & 0.1 & \textit{REVISE} & -14.6 & 12.2 \\
  vanilla & 0.1 & \textit{ECCo} & -4.34 & 3.58 \\
  vanilla & 0.1 & \textit{Generic} & -4.41 & 3.48 \\
  vanilla & 0.1 & \textit{REVISE} & -4.93 & 4.24 \\\bottomrule

\paragraph{Moons}\label{moons}

>>>>

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

@@

@@

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, titlerule=0mm, coltitle=black, left=2mm, bottomtitle=1mm, breakable, opacityback=0, rightrule=.15mm, toptitle=1mm, arc=.35mm, bottomrule=.15mm, colback=white, colframe=quarto-callout-note-color-frame, opacitybacktitle=0.6]

Figure~\ref{fig-mnist} shows much more plausible (faithful)
counterfactuals for a model with CT than the model with conventional
training (Figure~\ref{fig-mnist-vanilla}). In fact, this is not even
using \emph{ECCo+} and still showing better results than the best
results we achieved in our AAAI paper for JEM ensembles.

@@

\subsection{Grid Searches}\label{sec-app-grid}

@@

The hyperparameter grid with varying generator parameters during
training is shown in Parameters~\ref{exr-gen-params-final-run-train}.
The corresponding evaluation grid used for these experiments is shown in
Parameters~\ref{exr-gen-params-final-run-eval}.

\begin{exercise}[Training
Phase]\protect\hypertarget{exr-gen-params-final-run-train}{}\label{exr-gen-params-final-run-train}

@@

  \begin{itemize}
  \tightlist
  \item
    Decision Threshold: \texttt{0.75,\ 0.9,\ 0.95}
  \item
    \(\lambda_{\text{cost}}\): \texttt{0.001}
  \item
    \(\lambda_{\text{energy}}\): \texttt{0.1,\ 0.5,\ 5.0,\ 10.0,\ 20.0}
  \item
    Learning Rate: \texttt{0.25}
  \item
    Maximum Iterations: \texttt{5,\ 25,\ 50}
  \item
    Optimizer: \texttt{sgd}
  \end{itemize}
\item
  Generator: \texttt{ecco,\ generic,\ revise}
\item
  Model Parameters:

  \begin{itemize}
  \tightlist
  \item
    Activation: \texttt{relu}
  \item
    No.~Hidden: \texttt{32}
  \item
    No.~Layers: \texttt{1}
  \end{itemize}
\item
  Model: \texttt{mlp}
\item
  Training Parameters:

  \begin{itemize}
  \tightlist
  \item
    Burnin: \texttt{0.0}
  \item
    Class Loss: \texttt{logitcrossentropy}
  \item
    Convergence: \texttt{threshold}
  \item
    \(\lambda_{\text{adv}}\): \texttt{0.25}
  \item
    \(\lambda_{\text{yloss}}\): \texttt{1.0}
  \item
    \(\lambda_{\text{div}}\): \texttt{0.5}
  \item
    \(\lambda_{\text{reg}}\): \texttt{0.01}
  \item
    Learning Rate: \texttt{0.001}
  \item
    No.~Counterfactuals: \texttt{1000}
  \item
    No.~Epochs: \texttt{100}
  \item
    No.~Neighbours: \texttt{100}
  \item
    Objective: \texttt{full,\ vanilla}
  \item
    Optimizer: \texttt{adam}
  \end{itemize}
\end{itemize}

@@

\begin{exercise}[Evaluation
Phase]\protect\hypertarget{exr-gen-params-final-run-eval}{}\label{exr-gen-params-final-run-eval}

@@

  \begin{itemize}
  \tightlist
  \item
    Convergence: \texttt{threshold}
  \item
    Decision Threshold: \texttt{0.95}
  \item
    Maximum Iterations: \texttt{50}
  \item
    No.~Individuals: \texttt{100}
  \item
    No.~Runs: \texttt{5}
  \end{itemize}
\item
  Generator Parameters:

  \begin{itemize}
  \tightlist
  \item
    Decision Threshold: \texttt{0.75}
  \item
    \(\lambda_{\text{cost}}\): \texttt{0.0}
  \item
    \(\lambda_{\text{energy}}\): \texttt{0.1,\ 0.5,\ 1.0,\ 5.0,\ 10.0}
  \item
    Learning Rate: \texttt{0.25}
  \item
    Maximum Iterations: \texttt{30}
  \item
    Optimizer: \texttt{sgd}
  \end{itemize}
\end{itemize}

@@

\subsubsection{High-Level Findings}\label{high-level-findings}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/gen_params/mlp/moons/evaluation/results/ce/decision_threshold_exper---lambda_energy_exper---maxiter_exper---maxiter---decision_threshold_exper/plausibility_distance_from_target.png}}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/gen_params/mlp/moons/evaluation/results/ce/decision_threshold_exper---lambda_energy_exper---maxiter_exper---maxiter---decision_threshold_exper/distance.png}}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/gen_params/mlp/moons/evaluation/results/logs/objective---lambda_energy---generator_type---maxiter/percent_valid.png}}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/gen_params/mlp/moons/evaluation/results/logs/objective---lambda_energy---generator_type---maxiter/acc_val.png}}

\subsubsection{Detailed Findings}\label{detailed-findings}

@@

\begin{longtable}{cccccc}

@@

  \toprule
  \textbf{Decision Threshold} & \textbf{Lambda Energy} & \textbf{Maximum Iterations} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Decision Threshold} & \textbf{Lambda Energy} & \textbf{Maximum Iterations} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{6}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  0.75 & 0.1 & 5 & \textit{ECCo} & -15.9 & 16.7 \\
  \color{green}{\textbf{0.75}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{5}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{41.9}} & \color{green}{\textbf{8.13}} \\
  0.75 & 0.1 & 5 & \textit{REVISE} & -64.4 & 3.58 \\
  \color{green}{\textbf{0.75}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{28.9}} & \color{green}{\textbf{2.28}} \\
  0.75 & 0.1 & 25 & \textit{Generic} & -11.3 & 11.5 \\
  0.75 & 0.1 & 25 & \textit{REVISE} & -55.3 & 4.18 \\
  \color{green}{\textbf{0.75}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{50}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{10.9}} & \color{green}{\textbf{7.47}} \\
  0.75 & 0.1 & 50 & \textit{Generic} & -32.3 & 16.6 \\
  0.75 & 0.1 & 50 & \textit{REVISE} & -44.1 & 4.24 \\
  0.9 & 0.1 & 5 & \textit{ECCo} & -13.7 & 13.7 \\
  \color{green}{\textbf{0.9}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{5}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{22.3}} & \color{green}{\textbf{4.87}} \\
  0.9 & 0.1 & 5 & \textit{REVISE} & -27.8 & 6.26 \\
  0.9 & 0.1 & 25 & \textit{ECCo} & 8.84 & 7.13 \\
  \color{green}{\textbf{0.9}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{25}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{30.7}} & \color{green}{\textbf{5.77}} \\
  0.9 & 0.1 & 25 & \textit{REVISE} & -72.7 & 34.9 \\
  \color{green}{\textbf{0.9}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{50}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{17.1}} & \color{green}{\textbf{7.98}} \\
  0.9 & 0.1 & 50 & \textit{Generic} & 3.82 & 8.86 \\
  0.9 & 0.1 & 50 & \textit{REVISE} & -45.8 & 2.79 \\
  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{5}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{35.7}} & \color{green}{\textbf{7.56}} \\
  0.95 & 0.1 & 5 & \textit{Generic} & -13.3 & 5.73 \\
  0.95 & 0.1 & 5 & \textit{REVISE} & -54.9 & 5.43 \\
  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{37}} & \color{green}{\textbf{5.31}} \\
  0.95 & 0.1 & 25 & \textit{Generic} & 29 & 8.6 \\
  0.95 & 0.1 & 25 & \textit{REVISE} & -40.5 & 41 \\
  0.95 & 0.1 & 50 & \textit{ECCo} & 13.2 & 4.89 \\
  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.1}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{35.5}} & \color{green}{\textbf{4.27}} \\
  0.95 & 0.1 & 50 & \textit{REVISE} & -60.4 & 45.8 \\
  \color{red}{\textbf{0.75}} & \color{red}{\textbf{0.5}} & \color{red}{\textbf{5}} & \color{red}{\textbf{ECCo}} & \color{red}{\textbf{-0.94}} & \color{red}{\textbf{17.6}} \\
  0.75 & 0.5 & 5 & \textit{Generic} & -11.7 & 17.4 \\
  0.75 & 0.5 & 5 & \textit{REVISE} & -37.7 & 3.92 \\
  0.75 & 0.5 & 25 & \textit{ECCo} & 14.7 & 6.32 \\
  \color{green}{\textbf{0.75}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{25}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{32.3}} & \color{green}{\textbf{3.49}} \\
  0.75 & 0.5 & 25 & \textit{REVISE} & -39.9 & 7.21 \\
  \color{green}{\textbf{0.75}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{50}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{28.3}} & \color{green}{\textbf{5.05}} \\
  0.75 & 0.5 & 50 & \textit{Generic} & -9.72 & 9.19 \\
  0.75 & 0.5 & 50 & \textit{REVISE} & -30 & 5.22 \\
  0.9 & 0.5 & 5 & \textit{ECCo} & -7.38 & 13.6 \\
  \color{red}{\textbf{0.9}} & \color{red}{\textbf{0.5}} & \color{red}{\textbf{5}} & \color{red}{\textbf{Generic}} & \color{red}{\textbf{-0.0952}} & \color{red}{\textbf{17.1}} \\
  0.9 & 0.5 & 5 & \textit{REVISE} & -50.6 & 4.77 \\
  \color{green}{\textbf{0.9}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{39.1}} & \color{green}{\textbf{8.3}} \\
  0.9 & 0.5 & 25 & \textit{Generic} & 38.6 & 6.03 \\
  0.9 & 0.5 & 25 & \textit{REVISE} & -56.9 & 4.28 \\
  0.9 & 0.5 & 50 & \textit{ECCo} & -6.53 & 10.9 \\
  \color{green}{\textbf{0.9}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{13.6}} & \color{green}{\textbf{12.8}} \\
  0.9 & 0.5 & 50 & \textit{REVISE} & -24.1 & 12.5 \\
  0.95 & 0.5 & 5 & \textit{ECCo} & 0.596 & 1.11 \\
  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{5}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{4.57}} & \color{green}{\textbf{5.88}} \\
  0.95 & 0.5 & 5 & \textit{REVISE} & -34.3 & 6.09 \\
  0.95 & 0.5 & 25 & \textit{ECCo} & 16.5 & 3.53 \\
  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{25}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{19.1}} & \color{green}{\textbf{4.43}} \\
  0.95 & 0.5 & 25 & \textit{REVISE} & -37.2 & 39.2 \\
  0.95 & 0.5 & 50 & \textit{ECCo} & -31 & 14.2 \\
  \color{green}{\textbf{0.95}} & \color{green}{\textbf{0.5}} & \color{green}{\textbf{50}} & \color{green}{\textbf{Generic}} & \color{green}{\textbf{24.8}} & \color{green}{\textbf{4.78}} \\
  0.95 & 0.5 & 50 & \textit{REVISE} & -1.28 & 2.7 \\
  \color{green}{\textbf{0.75}} & \color{green}{\textbf{5}} & \color{green}{\textbf{5}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{37}} & \color{green}{\textbf{9.21}} \\
  0.75 & 5 & 5 & \textit{Generic} & 0.977 & 21.1 \\
  0.75 & 5 & 5 & \textit{REVISE} & -55.2 & 4.75 \\
  \color{green}{\textbf{0.75}} & \color{green}{\textbf{5}} & \color{green}{\textbf{25}} & \color{green}{\textbf{ECCo}} & \color{green}{\textbf{21.8}} & \color{green}{\textbf{5.97}} \\
  0.75 & 5 & 25 & \textit{Generic} & 17.8 & 5.33 \\
